MLH1 Data Report

### 2018-04-03 Main_Report.rmd
edits to report

@@

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green","purple","grey1", "grey" ))
ff <- ff   + facet_wrap(~ sex, scales="free")

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green", "purple","grey1","grey" ))
ss <- ss   + facet_wrap(~ sex, scales="free")

>>>>

#try to make sure sacles are the same

@@

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain ))+geom_boxplot()+ ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green","purple","grey1", "grey" )) +
 ylim( c((min(MLH1_data$adj_nMLH1.foci)-3) ), (max(MLH1_data$adj_nMLH1.foci)+5))
ff <- ff   + facet_wrap(~ sex, scales="free")

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00","red", "yellowgreen", "green", "purple","grey1","grey" )) +
  ylim( c( (min(MLH1_data$adj_nMLH1.foci)-3), (max(MLH1_data$adj_nMLH1.foci)+5)) )

ss <- ss   + facet_wrap(~ sex, scales="free")
